lab_notebook

### 2018-11-15 lab_notebook.Rmd
updated turf/itq data finished

@@

```{r}

# create dataframe with 
itq <- ITQ_projection %>%
  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")

@@

```{r}

@@

#change "blank" NAs to real NAs
all_turf_1[is.na(all_turf_1)] <- "NA"

#rearrange columns
all_turf_2 <- all_turf_1[, c(1,3,2,5,6,7,8,4)]

#turning NAs from no ITQ data to FALSE
#all_turf_2$itq_now[all_turf_2$itq_now == 0] <- NA

#all_turf_2 %>% replace(is.na(.), FALSE)

#doublecheckworked <- all_turf_2 %>%
#  filter( itq_now == "1" & turf == "TRUE")

>>>>

#create RDS from dataframe
#saveRDS(ITQ_projection, "ITQ_projection")

@@

#load data
```{r}

# create dataframe with 
ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")

itq <- ITQ_projection %>%
  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")

@@

#data wrangling
```{r}

@@

#change "blank" NAs to real NAs
#all_turf_1[is.na(all_turf_1)] <- "NA"

#rearrange columns
all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]

#turning NAs from no ITQ data to FALSE
#all_turf_2[all_turf_2 == 0] <- NA

all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE

all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE

all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE

all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0

#create RDS from dataframe
#saveRDS(all_turf_itq, "all_turf_itq.rds")
#write.csv(all_turf_itq, file = "all_turf_itq.csv")
